Introduction to Structural Causal Models

### 2021-05-21 presentation_video.Rmd
stuff

- Nonparametric SEM 
- System of equations with functions
- **Assignments** ':=' (non-symmetric) 
- algebraic equation '=' (symmetry)
**Error in Regression:** Omittable outside factor 
**Error in SCM:** Latent (influential) factor that is pivotal for the model

>>>>

- Nonparametric SEM 
- System of equations with functions
- **Assignments** ':=' (non-symmetric) 
- algebraic equation '=' (symmetry)
- **Error in Regression:** Omittable outside factor 
- **Error in SCM:** Latent (influential) factor that is pivotal for the model
